### 2022-05-15 manuscript/manuscript.Rmd
add table for conference abstract

>>>>

```{r}
# table for Peer Review Congress abstract

# summarise number of journals offering each PPPR type in each domain
sum_domain_type <- d_policy %>%
  count(domain, type = PPPR_name_harmonized, .drop = F) %>%
  filter(type %notin% c('Not categorised','Other'))

# summarise number of journals offering any PPPR type in each domain
sum_domain_any_type <- d_policy %>%
  filter(PPPR_type == 'A') %>% # only need the first entry for each journal
  count(domain, anyPPPR) %>%
  group_by(domain) %>%
  mutate(N = sum(n)) %>%
  filter(anyPPPR == T) %>%
  select(-anyPPPR) %>%
  mutate(type = 'Any PPPR')

sum_domain <- full_join(sum_domain_type, sum_domain_any_type %>% select(-N)) %>%
  right_join(sum_domain_any_type %>% select(domain, N), by = 'domain')

sum_overall <- sum_domain %>%
    group_by(type) %>%
    summarise(n = sum(n),
           N = sum(N)) %>%
    mutate(domain = 'All')

sum_combined <- bind_rows(sum_domain, sum_overall) %>%
  mutate(
    domain = factor(domain, 
                    levels = c('All', 
                               'HEALTH & LIFE SCIENCES',
                               'MULTIDISCIPLINARY',
                               'PHYSICAL SCIENCES',
                               'FORMAL SCIENCES',
                               'SOCIAL SCIENCES')),
    values = paste0(n,' (',round(n/N*100,0),'%)')) %>%  # add percentages
  select(-n) %>%
  rename('Features' = type)

# now do length and time limits
df_limits <- d_policy %>% 
  filter(!is.na(PPPR_name)) %>% 
  mutate(hasLengthLimit = ifelse(wordLimits %in% c('NOT STATED', 'NO'), F, T),
         hasTimeLimit = ifelse(timeLimits %in% c('NOT STATED', 'NO'), F, T),
         hasLengthLimit_quant = ifelse(wordLimits %in% c('NOT STATED', 'NO', 'Qualitative limit'), F, T),
         hasTimeLimit_quant = ifelse(timeLimits %in% c('NOT STATED', 'NO', 'Qualitative limit'), F, T),
         wordLimits = ifelse(
      wordLimits %in% c('Qualitative limit','NOT STATED', 'NO'), NA, as.numeric(wordLimits)),
    timeLimits = ifelse(
      timeLimits %in% c('Qualitative limit','NOT STATED', 'NO'), NA, as.numeric(timeLimits)))

df_limits_domain <- df_limits %>%
  group_by(domain) %>%
  summarise(
    across(c(hasLengthLimit, hasLengthLimit_quant, hasTimeLimit, hasTimeLimit_quant), sum),
    across(c(wordLimits, timeLimits), 
           list(median = median,
               IQR = ~ paste0(quantile(.x,na.rm=T)[2],'-',quantile(.x,na.rm=T)[4])), na.rm = T))

df_limits_overall <- df_limits %>%
  summarise(
    across(c(hasLengthLimit, hasLengthLimit_quant, hasTimeLimit, hasTimeLimit_quant), sum),
    across(c(wordLimits, timeLimits), 
           list(median = median,
               IQR = ~ paste0(quantile(.x,na.rm=T)[2],'-',quantile(.x,na.rm=T)[4])), na.rm = T)) %>%
  mutate(domain = 'All')

df_limits_combined <- bind_rows(df_limits_domain, df_limits_overall) %>%
  mutate(lengthLimits = paste0('Any: ', hasLengthLimit,' Quant: ', hasLengthLimit_quant),
         lengthQuant = paste0('Md = ', wordLimits_median, ' IQR: ', wordLimits_IQR),
         timeLimits = paste0('Any: ', hasTimeLimit,' Quant: ', hasTimeLimit_quant),
         timeQuant = paste0('Md = ', timeLimits_median, ' IQR: ', timeLimits_IQR)) %>%
  select(domain, lengthLimits, lengthQuant, timeLimits, timeQuant) %>% 
  pivot_longer(cols = lengthLimits:timeQuant, names_to = 'Features', values_to = 'values')

# PPPR prevalence by domain
prevalence_domain <- d_freq_primary %>% 
  mutate(linkedPPPR = factor(linkedPPPR)) %>% 
  count(domain, linkedPPPR, .drop = F) %>% 
  group_by(domain) %>% 
  mutate(N = sum(n)) %>% 
  filter(linkedPPPR == 'TRUE') %>%
  adorn_totals(where = 'row', name = 'All', "n", "N") %>%
  select(-linkedPPPR) %>%
  rowwise() %>%
  mutate(
    percent = round(n/N*100,1),
    ci_lwr = round(prop.test(n,N)$conf.int*100,1)[1],
    ci_upr = round(prop.test(n,N)$conf.int*100,1)[2],
    values = paste0(n,'/',N,', ',percent,'% (',ci_lwr,'-',ci_upr,'%)')
  ) %>%
  select(domain, values) %>%
  mutate('Features' = 'PPPR Prevalence')

# combine everything to make final table
final_table <-bind_rows(sum_combined, prevalence_domain, df_limits_combined) %>%
  select(-N) %>%
  right_join(sum_domain_any_type %>% ungroup() %>% select(domain, N) %>% add_row(domain = 'All', N = 330), by = 'domain') %>%
  pivot_wider(id_cols = Features,
              names_from = c(domain, N),
              values_from = c(values),
              names_glue = "{domain} (N={N})") %>%
  relocate('Features', 'All (N=330)', 'HEALTH & LIFE SCIENCES (N=165)', 'MULTIDISCIPLINARY (N=15)', 'PHYSICAL SCIENCES (N=90)', 'FORMAL SCIENCES (N=30)', 'SOCIAL SCIENCES (N=30)')

d_policy %>%
  mutate(limits = timeLimits) %>% # use either wordLimits or timeLimits
  filter(!is.na(PPPR_name), limits %notin% c('Qualitative limit','NOT STATED', 'NO')) %>%
  mutate(limits = as.numeric(limits)) %>%
  group_by(field) %>%
  summarise(
    md = median(limits),
    iqr = paste0(quantile(limits,na.rm=T)[2],'-',quantile(limits,na.rm=T)[4]),
    min = min(limits),
    max = max(limits)
  )

```
